What Variables Impact Wicket Production in the IPL

### 2024-12-13 paper/paper.qmd
fixed graph captions

```{r}
#| label: fig-runrate-numofwickets
#| fig-cap: Current Run Rate Does Not Impact Wicket Rate
#| echo: false
#| warning: false

@@

From @fig-runrate-numofwickets, both the distribution of current run rates of teams when a wicket occurs and when a wicket does not occur are approximately normally distributed around 8.5. The variability for both distributions also appears to be the same. However, the distribution of run rate for balls that are not wickets occur has more outliers than for wickets occurrences.

@@

```{r}
#| label: fig-bowlingstyle-wickets
#| fig-cap: Wickets are more likely later in the innings
#| echo: false
#| warning: false

@@

>>>>

### Wickets and Run Rate

```{r}
#| label: fig-runrate-numofwickets
#| fig-cap: Current Run Rate is Not Associated With Wicket Production
#| echo: false
#| warning: false

@@

From @fig-runrate-numofwickets, both the distribution of current run rates of teams when a wicket occurs and when a wicket does not occur are approximately normally distributed around a 8.5 run rate. The variability for both distributions also appears to be the same. However, the distribution of run rate for balls that are not wickets occur has more outliers than for wickets occurrences.

### Wickets and Over

@@

### Wickets Based on Batsman Bowler Matchup

```{r}
#| label: fig-bowlingstyle-wickets
#| fig-cap: Fast Bowlers Generate More Wickets
#| echo: false
#| warning: false

@@

### Wickets and Number of Wickets in the Previous Over
